### 2013-10-24 plan.tex
cleaned up phrasing

We propose a verified compiler for a language similar to typed CoreML$^2$\
cite{InfoFlowML}, targeting a simple register transfer level (RTL) language.  
We will construct this compiler in the Coq proof assistant\cite{coqart}, 
which allows extraction to OCAML\cite{berghofer2004extracting}.

This will allow us to take the first step towards a verified compiler
for a language with static information flow types such as
Jif\cite{myers1999jflow} or
FlowCaml\cite{simonet2003flow,simonet2003flowmanual}.  Developing a
verified compiler for such languages removes the need for programmers to
trust the compiler; to convince themselves that the compiler preserves 
the semantics and enforces properties (such as non-interference) of the 
source program they can verify the proofs used to generate
the compiler.  This eliminates the possibility of a compiler
introducing bugs during the translation of the source program, such
as additional undesirable information flows.  As a result, this compiler
reduces the trusted computing base from a large complex compiler to a
much simpler verifier to mechanically check the proofs from which 
the compiler is extracted.

To develop this verified compiler using Coq we plan to write formal
proofs which show that the type system correctly enforces non-interference
and that a CPS conversion\cite{appel2007compiling}, which would be our
approach to compiling the language to an RTL language, correctly
preserves the semantics of the source program.  We expect the proof
that the type system enforces non-interference will be very similar to
the proof presented in Pottier and Simonet's paper\cite{InfoFlowML}.
Development will proceed by first writing the proof for CPS conversion,
developing a compiler for the language without enforcing the type
system, and then going back and adding the non-interference proof.

>>>>

We propose a verified compiler for a language similar to typed CoreML$^2$
\cite{InfoFlowML}, targeting a simple register transfer level (RTL) language.  
We will construct this compiler in the Coq proof assistant\cite{coqart}, 
which allows the extraction of verified code to OCAML\cite{berghofer2004extracting}.

This will allow us to take the first step towards a verified compiler
for a language with static information flow types such as
Jif\cite{myers1999jflow} or
FlowCaml\cite{simonet2003flow,simonet2003flowmanual}.  Developing a
verified compiler for such languages removes the need for programmers to
trust the compiler; users can convince themselves of the compiler's 
correctness by verifying the proofs used to generate the compiler.
This eliminates the possibility of a compiler
introducing bugs during the translation of the source program, such
as additional undesirable information flows.  As a result, this compiler
reduces the trusted computing base from a large complex compiler to a
much simpler verifier to mechanically check the proofs from which 
the compiler is extracted.

To develop this verified compiler using Coq we plan to write formal
proofs which show that the type system correctly enforces non-interference
and that a CPS conversion\cite{appel2007compiling}, which would be our
approach to compiling the language to an RTL language, correctly
preserves the semantics of the source program.  We expect the proof
that the type system enforces non-interference will be very similar to
the proof presented in Pottier and Simonet's paper\cite{InfoFlowML}.
Development will proceed by first writing the proof for CPS conversion,
developing a compiler for the language without enforcing the type
system, and then going back and adding the non-interference proof.
We plan to target CompCert's RTL intermediate language.
